Casual Bandits

### 2016-01-18 causal-bandit/icml-2015/setup.tex
Moved key insight bit into setup.

>>>>

From a causal perspective the key insight is that the assumed causal structure implies that
the law of $Y_t$ given we intervene to set $X_{t,i} = j$ is the same as the law of $Y_t$ conditioned
on $X_{t,i} = j$. Formally,
\eqn {
\label{eq:observe}
\P{Y_t \leq y|do(X_{t,i} = j)} = \P{Y_t \leq y|do(),X_{t,i} = j}\,.
}
This follows from application of the do-calculus \cite{Pearl2000} to our specific causal graph. It is not the case in general. 
For example if there was a variable $X'$ that caused both $X_{t,i}$ and $Y$ (or $X_{t,i}$ and any other variable $X_{t,l}$), 
that would introduce a backdoor path from $X_{t,i} \rightarrow Y_t$ and we would have to condition on $X'$ to derive the 
interventional distribution of $Y_t$ from the observational one.

\todot{Or just give a reference or hide in the appendix depending on space in the end}
\color{red} Probably should define causal model and back-door rule to properly show this.\color{black}

We can also learn about the reward for intervening on one variable from rounds in which we actually set a different variable.

\eqn {
\label{eq:estimation_transfer}
P(Y_t|do(X_{t,i} = j))= & \nonumber \\
 \sum_{j'}  P(Y_t|do(X_{t,l} & = j'),X_{t,i} = j)P(X_{t,l} = j')
}

### 2016-01-18 causal-bandit/icml-2015/simple-regret.tex
updates
Moved key insight bit into setup.

From a causal perspective the key insight is that the assumed causal structure implies that
the law of $Y_t$ given we intervene to set $X_{t,i} = j$ is the same as the law of $Y_t$ conditioned
on $X_{t,i} = j$. Formally,
\eqn {
\label{eq:observe}
\P{Y_t \leq y|do(X_{t,i} = j)} = \P{Y_t \leq y|do(),X_{t,i} = j}\,.
}
This follows from application of the do-calculus \cite{Pearl2000} to our specific causal graph. It is not the case in general. 
For example if there was a variable $X'$ that caused both $X_{t,i}$ and $Y$ (or $X_{t,i}$ and any other variable $X_{t,l}$), 
that would introduce a backdoor path from $X_{t,i} \rightarrow Y_t$ and we would have to condition on $X'$ to derive the 
interventional distribution of $Y_t$ from the observational one.

\todot{Or just give a reference or hide in the appendix depending on space in the end}
\color{red} Probably should define causal model and back-door rule to properly show this.\color{black}

We can also learn about the reward for intervening on one variable from rounds in which we actually set a different variable.

\eqn {
\label{eq:estimation_transfer}
P(Y_t|do(X_{t,i} = j))= & \nonumber \\
 \sum_{j'}  P(Y_t|do(X_{t,l} & = j'),X_{t,i} = j)P(X_{t,l} = j')
}

@@

\begin{definition}
Let $\boldsymbol{q} \in [0,1]^N$. Then define $q^{(i)}$ to be the $i$th largest value of the set $\set{\min \set{q_j, 1 - q_j} : 1 \leq j \leq N}$.
For example, if $\boldsymbol{q} = (0,\, 2/3,\, 1/2)$, then $q^{(1)} = 0$, $q^{(2)} = 1/3$, $q^{(3)} = 1/2$.
Then define 
\eqn{
\label{def:m}
m(\boldsymbol{q}) = \min\set{1 \leq i \leq N: q^{(i+1)} \geq \frac{1}{i}}\,.
}
\end{definition}

\begin{theorem}\label{thm:unknown_q_simpleregret}
Algorithm \ref{alg:simple} satisfies
\eq{
\simpleregret \in \bigo{\sqrt{\frac{m}{T}\log\left(\frac{NT}{m}\right)}}\,.
}
\end{theorem}

>>>>

@@

\begin{definition}
Let $\boldsymbol{q} \in [0,1]^N$. Then define $q^{(i)}$ to be the $i$th largest value of the set $\set{\min \set{q_j, 1 - q_j} : 1 \leq j \leq N}$.
For example
\eq{
\boldsymbol{q} &= (0,\, 2/3,\, 1/2,\, 1) \\
q^{(1)} &= 0,\,\, q^{(2)} = 0,\,\, q^{(3)} = 1/3,\,\, q^{(4)} = 1/2\,.
}
Define 
\eqn{
\label{def:m}
m(\boldsymbol{q}) = \min\set{1 \leq i \leq N: q^{(i+1)} \geq \frac{1}{i}}\,.
}
\end{definition}

\begin{theorem}\label{thm:uq-simple}
Algorithm \ref{alg:simple} satisfies
\eq{
\simpleregret \in \bigo{\sqrt{\frac{m}{T}\log\left(\frac{NT}{m}\right)}}\,.
}
\end{theorem}
